Simulating the Linux page cache in distributed applications with the WRENCH library

### 2020-12-09 paper_io_sim.tex

        In this paper, we propose a I/O simulation model that characterizes the key features of the page cache.
        We have implemented the model with SimGrid, a simulation framework for 
        distributed systems, using WRENCH, a SimGrid-based workflow simulator. 
        Our simulator is compatible with both single-threaded and multithreaded applications,
        and can simulate both writeback and writethrough cache that can factor into local
        and network-based filesystems.
		The results show that our simulator not only achieves higher accuracy than 
		original WRENCH, but also effectively simulates memory contents and 
		page cache during I/O operations. 
		Through this study, our effort is to contribute an analytical model 
		of the page cache, which can also be integrated to other simulators 
		to improve I/O simulation accuracy.

>>>>

        In this paper, we propose a I/O simulation model that characterizes the key features of the page cache.
        We have implemented the model with SimGrid, a simulation framework for 
        distributed systems, using WRENCH, a SimGrid-based workflow simulator. 
        Our simulator is compatible with both single-threaded and multithreaded applications,
        and can simulate both writeback and writethrough cache that can factor into local
        and network-based filesystems.
